Adopting agile in the large: motivations, success factors and challenges

### 2013-01-26 tex/article.tex
Better articulating "what is large scale"

The selection process of the primary studies is summarized in Figure
\ref{fig:selection_process}. The database search yielded 1603 matches which were
filtered down to 31 selected primary studies. One study was not available, which
reduced the final number of primary studies to 30.
The primary studies were selected by four criteria: study type, size of
organization, use of agile methods in software development, and a transformation
viewpoint. Firstly, only case studies and experience reports on agile software
development were included in this study. Papers discussing agile methods or
organizational transformation on as a general topic were left out. Secondly, the
size of the organization described in the included primary studies was to be
large enough to show the challenges of large scale agile development
\citegen{Lindvall2004}. Further, only studies discussing agile software
development were included, leaving out for instance studies on agile management.
Finally, the included studies had to provide a viewpoint on the adoption of
agile methods.

>>>>

The selection process of the primary studies is summarized in Figure
\ref{fig:selection_process}. The database search yielded 1603 matches which were
filtered down to 31 selected primary studies. One study was not available, which
reduced the final number of primary studies to 30.
The primary studies were selected by four criteria: study type, size of
organization, use of agile methods in software development, and a transformation
viewpoint. Firstly, only case studies and experience reports on agile software
development were included in this study. Papers discussing agile methods or
organizational transformation on as a general topic were left out. Secondly, the
papers had to indicate that the development organization is considered being
large (smallest included reported 50 persons). The presence of several
development teams also had to be indicated. Further, only studies discussing
agile software development were included, leaving out for instance studies on
agile management. Finally, the included studies had to provide a viewpoint on
the adoption of agile methods.
